\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}

\titleformat{\section}{\large\bfseries}{}{0em}{}
\titlespacing*{\section}{0pt}{1em}{0.3em}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.5em}

\begin{document}

\begin{center}
    {\LARGE \textbf{Getaway}}\\[0.3em]
    {\large CIS 5680 --- Group Game Project 2}
\end{center}

\section{High Concept}

An asymmetric co-op VR heist game where one player flees through city streets as a bank robber while a partner pilots a surveillance drone overhead, guiding the escape and sabotaging the police in real time.

\section{Genre}

Asymmetric cooperative VR action-stealth with bird's eye and worm's eye perspectives.

\section{Features}

\begin{itemize}[leftmargin=2em]
    \item \textbf{Two radically different perspectives.} The robber experiences the city in first-person at street level, ducking through alleys and crowds. The drone pilot views the same city from above as a living tactical map, seeing threats the robber cannot.

    \item \textbf{Cooperative communication is survival.} Neither player has the full picture alone. The drone pilot spots patrol routes and roadblocks; the robber sees ground-level shortcuts and hiding spots invisible from above. Success demands constant coordination.

    \item \textbf{Drone environmental interaction.} The overhead player isn't just watching --- they hack traffic lights to stall police cars, lock doors behind the robber to cut off pursuit, and trigger distractions like car alarms and fire hydrants to buy precious seconds.

    \item \textbf{Ground-level stealth tools.} The robber can snatch disguises from clotheslines and storefronts, blend into pedestrian crowds, and slip through building interiors that the drone's camera cannot penetrate.

    \item \textbf{Adaptive AI police.} Cops respond dynamically to the robber's last known position, setting up perimeters and calling in reinforcements. Predictable routes get punished; creative improvisation is rewarded.

    \item \textbf{Escalating heat system.} The longer the chase goes on, the more aggressive the response becomes --- from beat cops on foot to squad cars, helicopters, and eventually SWAT. Each heat level changes the tactics both players need.

    \item \textbf{Procedural city layouts.} Street configurations and patrol placements shuffle between rounds, preventing memorized routes and keeping every heist feeling fresh.

    \item \textbf{Race against the clock.} The team must reach the getaway vehicle before the timer expires. Faster escapes earn higher scores, encouraging replayability and speedrun competition.
\end{itemize}

\section{Player Challenge / Motivation}

One player is the robber: on the run, heart pounding, weaving through a hostile city with nothing but quick reflexes and a voice in their ear. The other is the drone pilot: calm, strategic, managing the chaos from above and clearing a path through the police net. Together they must outwit an ever-tightening pursuit to pull off the perfect escape.

\section{Design Goals}

\textbf{Cooperative tension.} The split perspectives create natural information asymmetry. Players feel genuinely dependent on each other, and every callout --- ``cop on your left,'' ``I just locked the gate behind you'' --- builds shared adrenaline.

\textbf{Replayability.} Procedural layouts, adaptive AI, and the escalating heat system mean no two escapes play out the same way. Players are motivated to retry for cleaner, faster getaways.

\textbf{Accessible asymmetry.} The drone role is less physically demanding and more strategic, making the game approachable for players of different comfort levels with VR while still being deeply engaging for both sides.

\section{Unique Selling Points}

\begin{itemize}[leftmargin=2em]
    \item \textbf{True asymmetric co-op in VR} with meaningfully different gameplay for each role, not just a camera angle swap. Each player has unique abilities and responsibilities.
    \item \textbf{Active drone interaction} elevates the overhead player from passive spotter to tactical partner who reshapes the environment in real time.
    \item \textbf{The heist-escape fantasy} is a universally understood power fantasy that hasn't been explored in asymmetric VR co-op, giving the game immediate hook and recognizability.
\end{itemize}

\end{document}
